Model \& Simulation of South Bend Government Call Center using Arena

### 2018-10-08 Paper.tex
prior work draft in there

\section{Background \& Terminology}
Call centers are a frequently studied topic within the simulation and modeling disciplines.  As such, some basic terminology shall be explained.  This model consists of two primary components:  calls and operators.  Calls will be represented as entities in Arena, as they are created and move through the system.  The operators, also known as ``311 liasons," will be represented as resources in Arena.

For this exploration, an ``arrival" is defined as a unique call first coming into the call process model.

@@

Call center and queuing analysis has been the focus of academic research for years.  Brown et al. provide an excellent overview of the Poisson distribution modeling customer arrivals, as well as the accompanying assumptions.  While arrival distribution is not analyzed in this paper, the authors' assumptions are, for the most part, assumed to be true in this analysis.  These center around the general assumption that the customers and operators are statistically identical and that they all act independently.\cite{brown}  Zhang, Hong, and Zhang also describe the arrival process as a Poisson distribution, but discuss models which may be more accurate alternatives.\cite{zhang}  They maintain some of the main assumptions as Brown.  As a result, differences in time-dependent parameters, customer attitudes and preferences, and operator skill levels are treated as negligible.
\par
Call centers are a prime opportunity to utilize simulation techniques.  In fact, according to Bapat and Pruitte, simulation is the preferred method to analyze and determine the effectiveness of a call center.\cite{bapat}  It allows for evaluation of metrics beyond what a basic analysis encompasses.  For example, the scheduling of call agents should be optimized against call duration and abandonment, as documented by Saltzman and Mehrota.\cite{saltzman}

@@

% I need to rework all of this shit
While such arrivals are frequently defined with an exponential distribution, this model utilizes a more accurate representation of arrivals as calculated from the aforementioned open-source data.

@@

\begin{thebibliography}{7}
\bibitem{baraka}
Baraka, H., Baraka H. \& El-Gamily, I. (2013). Assessing call centers' success: A validation of the DeLone and Mclean model for information system. \textit{Egyptian Informatics Journal, 14}, 99-108.

\bibitem{brown}
Brown, L., Gans, N., Mandelbaum, A., Sakov, A., Shen, H., Zeltyn, S., \& Zhao, L. (2005). Statistical analysis of a telephone call center: a queueing-science perspective. \textit{Journal of the American Statistical Association, 100(469)}, 36-50.

\bibitem{zhang}
Xiaowei Zhang, L. Jeff Hong, \& Jiheng Zhang. (2014). Scaling and modeling of call center arrivals. \textit{In Proceedings of the 2014 Winter Simulation Conference (WSC '14)}. IEEE Press, Piscataway, NJ, USA, 476-485.

\bibitem{bapat}
Vivek Bapat \& Eddie B. Pruitte, Jr.. (1998). Using simulation in call centers. \textit{In Proceedings of the 30th conference on Winter simulation (WSC '98)}, D. J. Medeiros, Edward F. Watson, John S. Carson, and Mani S. Manivannan (Eds.). IEEE Computer Society Press, Los Alamitos, CA, USA, 1395-1400.

\bibitem{saltzman}
Robert Saltzman \& Vijay Mehrotra. (2007). Managing trade-offs in call center agent scheduling: methodology and case study. \textit{In Proceedings of the 2007 Summer Computer Simulation Conference (SCSC '07)}. Society for Computer Simulation International, San Diego, CA, USA, 643-651.

\bibitem{mandelbaun}
Mandelbaun A., A. Sakov and S. Zeltyn. 2001. Empirical Analysis of a Call Center. Technion Israel Institute of Technology, Israel.

>>>>

\section{Background \& Terminology}
Call centers are a frequently studied topic within the simulation and modeling disciplines.  As such, some basic terminology shall be explained.  This model consists of two primary components:  calls and operators.  Calls will be represented as entities in Arena, as they are created and move through the system.  For this exploration, an ``arrival" is defined as a unique call first coming into the call process model.  The operators, also known as ``311 liasons," will be represented as resources in Arena.
\par
%more here
We need another background paragraph here
%more here

@@

Call center and queuing analysis has been the focus of academic research for years.  Brown et al. provide an excellent overview of the Poisson distribution modeling customer arrivals, as well as the accompanying assumptions.  While arrival distribution is analyzed directly from the data in this model, the authors' assumptions are, for the most part, assumed to be true in this analysis.  These center around the general assumption that the customers and operators are statistically identical and that they all act independently.\cite{brown}  Zhang, Hong, and Zhang also describe the arrival process as a Poisson distribution, but discuss models which may be more accurate alternatives.\cite{zhang}  They maintain some of the main assumptions as Brown.  As a result, differences in time-dependent parameters, customer attitudes and preferences, and operator skill levels are treated as negligible.
\par
Call centers are a prime opportunity to utilize simulation techniques.  In fact, according to Bapat and Pruitte, simulation is the preferred method to analyze and determine the effectiveness of a call center.\cite{bapat}  It allows for evaluation of metrics beyond what a basic analysis encompasses.  For example, the scheduling of call agents should be optimized against call duration and abandonment, as documented by Saltzman and Mehrota.\cite{saltzman}  Such simulations can easily be created to illustrate feasibility of goal accomplishment for corporations while enabling efficient and accurate decision-making.\cite{saltzmeh}

@@

% I need to rework all of this shit
While such arrivals are frequently defined with an exponential distribution, this model utilizes a more accurate representation of arrivals as calculated from the aforementioned open-source data.  The scheduling of operators (resources) is dedicated by the actual 311 call center schedule, showing in Figure 3.

@@

\newpage
\clearpage
\begin{thebibliography}{7}
\bibitem{baraka}
Baraka, H., Baraka H. \& El-Gamily, I. (2013). Assessing call centers' success: A validation of the DeLone and Mclean model for information system. \textit{Egyptian Informatics Journal, 14}, 99-108.

\bibitem{brown}
Brown, L., Gans, N., Mandelbaum, A., Sakov, A., Shen, H., Zeltyn, S., \& Zhao, L. (2005). Statistical analysis of a telephone call center: a queueing-science perspective. \textit{Journal of the American Statistical Association, 100}(469), 36-50.

\bibitem{zhang}
Zhang X., L. Jeff Hong, \& Jiheng Zhang. (2014). Scaling and modeling of call center arrivals. \textit{In Proceedings of the 2014 Winter Simulation Conference (WSC '14)}. IEEE Press, Piscataway, NJ, USA, 476-485.

\bibitem{bapat}
Bapat, V. \& Pruitte, E.B. Jr.. (1998). Using simulation in call centers. \textit{In Proceedings of the 30th conference on Winter simulation (WSC '98)}, D. J. Medeiros, Edward F. Watson, John S. Carson, and Mani S. Manivannan (Eds.). IEEE Computer Society Press, Los Alamitos, CA, USA, 1395-1400.

\bibitem{saltzman}
Saltzman, R. \& Mehrotra, V.. (2007). Managing trade-offs in call center agent scheduling: methodology and case study. \textit{In Proceedings of the 2007 Summer Computer Simulation Conference (SCSC '07)}. Society for Computer Simulation International, San Diego, CA, USA, 643-651.

\bibitem{saltzmeh}
Saltzman, R.M. \& Mehrota, V. (2001). A call center uses simulation to drive strategic change. \textit{Interfaces 31}(3). \href{https://doi.org/10.1287/inte.31.3.87.9632}{https://doi.org/10.1287/inte.31.3.87.9632}.

\bibitem{mandelbaun}
Mandelbaun A., A. Sakov and S. Zeltyn. (2001). Empirical Analysis of a Call Center. Technion Israel Institute of Technology, Israel.
